---
title: "Remote Covrpage"
author: "Jonathan Sidi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Snapshots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

When browsing GitHub for packages to install many times you want to kick the tires of the repository without wanting to _commit_ to it. 

`Covrpage` has your back. 

```{r}
library(covrpage)
```

## Test Plans

List of all the expectations defined in the `tests/testthat` directory.

```{r,include=FALSE}
testmap <- map_testthat_snapshot('tidyverse/purrr')
```

```{r,eval=FALSE}
testmap <- map_testthat_snapshot('tidyverse/purrr')
```
 

First five tests 
 
```{r}
knitr::kable(head(testmap,5))
```

<details><summary>Click to see the rest of the tests</summary>

```{r}
knitr::kable(tail(testmap,-5))
```

</details>

<br>

## Test Report

Run `covrpage` in a sterile environment to output the report `README`.

```{r,eval=FALSE}
covrpage_snapshot('tidyverse/purrr')
```
